{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-07-29 thesis/tm.tex
fix all the busted retry-set tests since i fixed the last(?) bug in it

\begin{table}[h]
	\begin{center}
		\footnotesize
		\begin{tabular}{cc||r|r||r|r||r|r}
			& & \multicolumn{2}{c||}{\bf Retry aborts only}
			  & \multicolumn{2}{c||}{\bf Retry sets ({\tt -R})}
			  & \multicolumn{2}{c}{\bf Abort codes ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size}
			  & \cpu{\bf cpu (s)} & \ints{\bf SS size}
			  & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.})
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.})
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt htm2}
			& 2,1 & \cpu{16.30}	& \ints{22}	& \cpu{19.82}	& \ints{17}	& \cpu{3.32}	& \ints{4} \\
			& 2,2 & \cpu{69.80}	& \ints{1970}	& \cpu{38.71}	& \ints{906}	& \cpu{26.59}	& \ints{288} \\
			& 2,3 &\cpu{3510.00}	& \ints{104914}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			%& 2,4 &	\ETAdag{...}	& \ETAdag{...}	\\
			& 3,1 &\cpu{41.07}	& \ints{941}	& \cpu{29.38}	& \ints{553}	& \cpu{23.03}	& \ints{162} \\
			& 3,2 &	\ETAdag{9d 19h}	& \ETAdag{5058149}	\\ % add 10h ok
			% [JOB 4] progress: 923822/5058149 brs (18.264030%), ETA 9d 8h 30m 38s (elapsed 9h 59m 55s)
			& 4,1 & \cpu{12699.65}	& \ints{344240}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			\hline
			{\tt counter}
			& 2,1 & \cpu{5.40}	& \ints{10}	& \cpu{6.70}	& \ints{8}	& \cpu{3.22}	& \ints{4} \\
			& 2,2 & \cpu{10.91}	& \ints{190}	& \cpu{14.91}	& \ints{288}	& \cpu{7.90}	& \ints{48} \\
			& 2,3 & \cpu{134.21}	& \ints{3970}	& \cpu{379.04}	& \ints{11512}	& \cpu{35.00}	& \ints{904} \\
			& 2,4 & \cpu{3009.40}	& \ints{86950}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 3,1 & \cpu{8.30}	& \ints{120}	& \cpu{8.90}	& \ints{74}	& \cpu{7.55}	& \ints{40} \\
			& 3,2 & \cpu{2038.90}	& \ints{60606}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 4,1 & \cpu{101.95}	& \ints{3006}	& \cpu{99.22}	& \ints{2854}	& \cpu{32.95}	& \ints{848} \\
			\hline
			{\tt swap}
			& 2,1 & \cpu{38.79}	& \ints{99}	& \cpu{35.80}	& \ints{84}	& \cpu{3.25}	& \ints{4} \\
			& 2,2 & \cpu{10299.27}	& \ints{233396}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 3,1 & \ETAdag{todo}	& \ETAdag{todo}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			\hline
			{\tt fig63}
			& 2,1 & \cpu{6.66}	& \ints{18}	& \cpu{6.50}	& \ints{6}	& \cpu{3.10}	& \ints{1} \\
			& 2,2 & \cpu{11.52}	& \ints{244}	& \cpu{10.74}	& \ints{192}	& \cpu{3.12}	& \ints{1} \\
			& 2,3 & \cpu{107.04}	& \ints{4428}	& \cpu{146.96}	& \ints{6151}	& \cpu{3.13}	& \ints{1} \\
			& 3,1 & \cpu{13.68}	& \ints{296}	& \cpu{7.29}	& \ints{21}	& \cpu{3.26}	& \ints{1} \\
			& 3,2 & \ETAdag{todo}	& \ETAdag{todo}	& \cpu{}	& \ints{}	& \cpu{3.35}	& \ints{1} \\
			& 4,1 & \cpu{220.27}	& \ints{7382}	& \cpu{11.40}	& \ints{157}	& \cpu{3.27}	& \ints{1} \\
			\hline
			{\tt avl\_insert}
			& 2,1 & \cpu{491.98}	& \ints{15056}	& \cpu{220.53}	& \ints{6332}	& \cpu{98.77}	& \ints{2776} \\
			% (2,2) - bug found on regular w/ 127 ints, on retry sets w/ 201 ints, and codes w/ 45 ints
			\hline
			{\tt avl\_fixed}
			& 2,1 & \cpu{572.49} 	& \ints{20420} 	& \cpu{271.11}	& \ints{9739}	& \cpu{99.16}	& \ints{2776} \\
			& 2,2 & \ETAdag{133y}	& \ETAdag{51484570} 	\\ % added 10hr but dosent matter
			% [JOB 19] progress: 408805/51484570 brs (0.794034%), ETA 132y 356d 8h 55m 16s (elapsed 9h 59m 19s)
			& 3,1 & \ETAdag{todo}	& \ETAdag{todo}	\\

			\hline
			{\tt map\_basic}
			& 2,1 & \ETAdag{todo} & \ETAdag{todo} \\
			\hline
			{\tt map\_basicer}
			& 2,1 & \cpu{36.17}& \ints{426}	\\ % TODO make sure this gets updated if you update the test
			& 2,2 & \ETAdag{todo} & \ETAdag{todo} \\
			& 3,1 & \ETAdag{todo} & \ETAdag{todo} \\
		\end{tabular}
	\end{center}
	\caption{Transactional tests verified (or not) by Landslide.
		Run with {\tt -M -X}, plus any additional reduction options listed.
		``Retry aborts only'' always tests every abort path without distinguishing among failure reasons;
		``Retry sets'' skips equivalent retry abort reorderings (\sect{\ref{sec:tm-retrysets}});
		``Abort codes'' suppresses retries and dynamically detects when to inject conflict aborts and so on
		(\sect{\ref{sec:txn-abort-codes}}).
		State space estimates measured after a timeout of 10 hours.
		}
	\label{tab:verifs}
\end{table}

>>>>

		\begin{tabular}{cc||r|r||r|r||r|r}
			& & \multicolumn{2}{c||}{\bf Retry aborts only}
			  & \multicolumn{2}{c||}{\bf Retry sets ({\tt -R})}
			  & \multicolumn{2}{c}{\bf Abort codes ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size}
			  & \cpu{\bf cpu (s)} & \ints{\bf SS size}
			  & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.})
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.})
			  & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			{\tt htm2}
			& 2,1 & \cpu{16.30}	& \ints{22}	& \cpu{17.93}	& \ints{15}	& \cpu{3.32}	& \ints{4} \\
			& 2,2 & \cpu{69.80}	& \ints{1970}	& \cpu{27.87}	& \ints{408}	& \cpu{26.59}	& \ints{288} \\
			& 2,3 &\cpu{3510.00}	& \ints{104914}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			%& 2,4 &	\ETAdag{...}	& \ETAdag{...}	\\
			& 3,1 &\cpu{41.07}	& \ints{941}	& \cpu{23.86}	& \ints{273}	& \cpu{23.03}	& \ints{162} \\
			& 3,2 &	\ETAdag{9d 19h}	& \ETAdag{5058149}	\\ % add 10h ok
			% [JOB 4] progress: 923822/5058149 brs (18.264030%), ETA 9d 8h 30m 38s (elapsed 9h 59m 55s)
			& 4,1 & \cpu{12699.65}	& \ints{344240}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			{\tt counter}
			& 2,1 & \cpu{5.40}	& \ints{10}	& \cpu{7.00}	& \ints{8}	& \cpu{3.22}	& \ints{4} \\
			& 2,2 & \cpu{10.91}	& \ints{190}	& \cpu{10.57}	& \ints{122}	& \cpu{7.90}	& \ints{48} \\
			& 2,3 & \cpu{134.21}	& \ints{3970}	& \cpu{85.29}	& \ints{2376}	& \cpu{35.00}	& \ints{904} \\
			& 2,4 & \cpu{3009.40}	& \ints{86950}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 3,1 & \cpu{8.30}	& \ints{120}	& \cpu{9.40}	& \ints{74}	& \cpu{7.55}	& \ints{40} \\
			& 3,2 & \cpu{2038.90}	& \ints{60606}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 4,1 & \cpu{101.95}	& \ints{3006}	& \cpu{82.16}	& \ints{2148}	& \cpu{32.95}	& \ints{848} \\
			{\tt swap}
			& 2,1 & \cpu{38.79}	& \ints{99}	& \cpu{37.33}	& \ints{59}	& \cpu{3.25}	& \ints{4} \\
			& 2,2 & \cpu{10299.27}	& \ints{233396}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			& 3,1 & \cpu{2359.85}	& \ints{59850}	& \cpu{}	& \ints{}	& \cpu{}	& \ints{} \\
			{\tt fig63}
			& 2,1 & \cpu{6.66}	& \ints{18}	& \cpu{6.98}	& \ints{6}	& \cpu{3.10}	& \ints{1} \\
			& 2,2 & \cpu{11.52}	& \ints{244}	& \cpu{8.75}	& \ints{76}	& \cpu{3.12}	& \ints{1} \\
			& 2,3 & \cpu{107.04}	& \ints{4428}	& \cpu{32.26}	& \ints{1060}	& \cpu{3.13}	& \ints{1} \\
			& 3,1 & \cpu{13.68}	& \ints{296}	& \cpu{7.55}	& \ints{21}	& \cpu{3.26}	& \ints{1} \\
			& 3,2 & \ETAdag{todo}	& \ETAdag{todo}	& \cpu{}	& \ints{}	& \cpu{3.35}	& \ints{1} \\
			& 4,1 & \cpu{220.27}	& \ints{7382}	& \cpu{11.13}	& \ints{130}	& \cpu{3.27}	& \ints{1} \\
			& 2,1 & \cpu{491.98}	& \ints{15056}	& \cpu{228.23}	& \ints{6296}	& \cpu{98.77}	& \ints{2776} \\
			% (2,2) - bug found on regular w/ 127 ints, on retry sets w/ 201 ints, and codes w/ 45 ints
			{\tt avl\_fixed}
			& 2,1 & \cpu{572.49} 	& \ints{20420} 	& \cpu{284.37}	& \ints{9685}	& \cpu{99.16}	& \ints{2776} \\
			& 2,2 & \ETAdag{133y 2d}	& \ETAdag{51484570} 	\\ % added 10hr but dosent matter
			% [JOB 19] progress: 408805/51484570 brs (0.794034%), ETA 132y 356d 8h 55m 16s (elapsed 9h 59m 19s)
			& 3,1 & \ETAdag{30y 320d}	& \ETAdag{93493027}	\\
			% [JOB 18] progress: 492976/93493027 brs (0.011233%), ETA 30y 319d 14h 48m 32s (elapsed 9h 59m 35s)
			{\tt map\_basic}
			& 2,1 & \ETAdag{todo} & \ETAdag{todo} \\
			{\tt map\_basicer}
			& 2,1 & \cpu{36.17}& \ints{426}	\\ % TODO make sure this gets updated if you update the test
			& 2,2 & \ETAdag{todo} & \ETAdag{todo} \\
			& 3,1 & \ETAdag{todo} & \ETAdag{todo} \\
	\caption{Transactional tests verified (or not) by Landslide.
		Run with {\tt -M -X}, plus any additional reduction options listed.
		``Retry aborts only'' always tests every abort path and does not distinguish among failure reasons,
		as the baseline;
		``Retry sets'' skips equivalent success path and/or retry abort reorderings (\sect{\ref{sec:tm-retrysets}});
		``Abort codes'' suppresses retries and dynamically detects when to inject conflict aborts and so on
		(\sect{\ref{sec:txn-abort-codes}}).
		State space estimates measured after a timeout of 10 hours.
	\label{tab:verifs}
